### 2018-05-02 paper/evaluation.tex

\begin{figure}[t]
\centering
\vspace{-1em}

$$A =
\kbordermatrix{
      & W   & O   & H   \cr
    W & 0.6 & 0.4 & 0   \cr
    O & 0.2 & 0.6 & 0.2 \cr
    H & 0   & 0.4 & 0.6 \\[0.3em]
}, \;
B = 
\kbordermatrix{
      & W     & O   & H   \cr
    p & 0.7 & 0.6 & 0.8 \cr
    w & 0.7 & 0   & 0   \cr
    h & 0   & 0   & 0.7 \cr
    l & 0.2 & 0.4 & 0.6 \\[0.3em]
}$$

\includegraphics[width=0.9\columnwidth]{figures/hmm.pdf}
\vspace{2ex}
\includegraphics[width=\columnwidth]{figures/sample_usage.pdf}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.8\columnwidth]{figures/nodes_per_layer_vs_theta.pdf}
\caption{\label{fig:nodes_per_layer_vs_theta}Number of nodes per layer of POR as a function of the parameter $\theta$ (the maximal probability that all nodes in a layer fail at once). The number of nodes logarithmically decreases as we relax the $\theta$ constraint.}
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figures/success_rate_vs_t.pdf}
\caption{\label{fig:success_rate_vs_t}Availability rate of routes as a function of the time since the route establishment, for several values of the parameters $\theta$ (the maximal probability that all nodes in a layer fail at once) and $L$ (the number of layers in the route).}
\end{figure}

@@

\newcommand{\fsize}{\ensuremath{s_f}}

To assess the efficiency of \name, we did several file exchanges with fixed parameters and a random file size $\fsize\in [5\text{MB}, 500\text{MB}]$. 
By performing 20 experiments using the parameters described in \ref{ssub:experimental_parameters}, we obtained traces for 200 file exchanges.

\begin{figure}[t]
\centering
\includegraphics[width=0.9\columnwidth]{figures/transfer_time_vs_size.pdf}

\caption{\label{fig:transfer_time_vs_size}Files' transfer time as a function of their size, along with a log-linear regression of the same data.}

\end{figure}

>>>>

\begin{figure}[t]
\centering
\vspace{-1em}
\footnotesize
\centering
$$A =
\kbordermatrix{
      & W   & O   & H   \cr
    W & 0.6 & 0.4 & 0   \cr
    O & 0.2 & 0.6 & 0.2 \cr
    H & 0   & 0.4 & 0.6 \\[0.3em]
}, \;
B = 
\kbordermatrix{
      & W     & O   & H   \cr
    p & 0.7 & 0.6 & 0.8 \cr
    w & 0.7 & 0   & 0   \cr
    h & 0   & 0   & 0.7 \cr
    l & 0.2 & 0.4 & 0.6 \\[0.3em]
}$$

\includegraphics[width=0.65\columnwidth]{figures/hmm.pdf}
\vspace{2ex}
\includegraphics[width=0.9\columnwidth]{figures/sample_usage.pdf}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.7\columnwidth]{figures/nodes_per_layer_vs_theta.pdf}
\caption{\label{fig:nodes_per_layer_vs_theta}Number of nodes per layer of POR as a function of the parameter $\theta$ (the maximal probability that all nodes in a layer fail at once). The number of nodes logarithmically decreases as we relax the $\theta$ constraint.}
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=0.9\columnwidth]{figures/success_rate_vs_t.pdf}
\caption{\label{fig:success_rate_vs_t}Availability rate of routes as a function of the time since the route establishment, for several values of the parameters $\theta$ (the maximal probability that all nodes in a layer fail at once) and $L$ (the number of layers in the route).}
\end{figure}

@@

To assess the efficiency of \name, we did several file exchanges with fixed parameters and a random file size between 5MB and 500MB.
By performing 20 experiments using the parameters described in \ref{ssub:experimental_parameters}, we obtained traces for 200 file exchanges.
All files reached their destination successfully.

\begin{figure}[t]
\centering
\includegraphics[width=0.7\columnwidth]{figures/transfer_time_vs_size.pdf}

\caption{\label{fig:transfer_time_vs_size}Files' transfer time as a function of their size, along with a log-linear regression of the same data.}
\end{figure}

Figure~\ref{fig:transfer_time_vs_size} shows the results of this experiment: it plots the transfer time as a function of the file size. File size is binned into 20 bins, making the series of points representing the average transfer time per bin with standard deviation bars.
We fitted a log-linear regression to this plot, displayed as a curve.
It shows that transfer time increases less fast that the file size.

Absolute time values are meaningless here: our system was evaluated on a single machine and on a single process. The code execution was not parallel, and only one device was executing at any point in time.

Still, we investigated the message transmission. In this simulation, 145172 chunks were sent, and 141276 ACKs were received: 6.00\% of the chunks were lost in transit. A chunk took an average of 56s $\pm$ 36s to reach its destination, while ACKs to 48s $\pm$ 33s to do so. This is explained mostly by devices falling offline between the time they receive a message and the time they forward it.

We now understand the log-linear curve and it's big initial slope: messages spend a long time in transit, but sending messages in parallel does not impact this time. Even small files thus need a lot of time to transfer, while bigger files do not suffer more than small files from the messages delay.
\\

Overall, we succeeded in creating a reliable and secure file transfer protocol over an underlying network of unreliable, low-end devices.
Its performance could be enhanced by taking interest in bottlenecks in the messages transmission, i.e. scheduling messages in a similar predictive manner as we planned routes creation.
